Transparent Standby for Low-Power, Resource-Constrained Embedded Systems

### 2018-02-17 LCTES/body.tex
(>) small adjusts

Figure~\ref{lst.adc} shows the driver for .

@@

output void ANALOG_REQUEST do
  <...>   // port manipulation to start the conversion
end

async/isr ADC_vect_num do
  var int value = <...>; // register with the value read
  emit ANALOG_DONE(value);
end

@@

\begin{figure}[t]
\begin{lstlisting}[numbers=left]
#define PM_GET(peripheral) \
        bitRead(pm, peripheral)
#define PM_SET(peripheral,state) \
        bitWrite(pm, peripheral, state)

>>>>

Figure~\ref{lst.adc} shows the driver for the A/D converter in \CEU.
For simplicity, we assume in the paper that the converter has a single channel
to avoid having to deal with multiplexing.
%
The driver exposes raw I/O events (ln. 3--4) that only deal with low-level
port manipulation in the microcontroller.
The output event (ln. 9--11)

@@

output void ANALOG_REQUEST do
  {
    ADMUX = 0x40 | (A0 & 0x07);
    bitSet(ADCSRA, ADIE); // enables interrupt
    bitSet(ADCSRA, ADSC); // starts the conversion
  }
end

async/isr ADC_vect_num do
  { bitClear(ADCSRA, ADIE); } // disables interrupt
  var int value = {ADC}; // register with the value read
  emit ANALOG_DONE(value);
end

@@

\begin{figure}[t]
\begin{lstlisting}[numbers=left]
#define PM_GET(dev)   bitRead(pm,dev)
#define PM_SET(dev,v) bitWrite(pm,dev,v)

### 2018-02-17 LCTES/lctes.tex
(>) small adjusts

\usepackage{listings}
\lstdefinelanguage{ceu}{%
  language=C,
  morekeywords={%
    and, uint32_t, code, async, isr,
    await, bool, call, class, data, define, deterministic, do, each, else,
    emit, end, escape, event, every, finalize, hor, implementation, in,
    input, interface, loop, min, native, new, nohold, not, or, output, par,
    pool, pure, return, signal, spawn, tag, then, this, traverse, until,
    var, watching, when, with},
}
\lstset{
  basicstyle=\ttfamily,
  captionpos=b,
  columns=flexible,
  commentstyle=\rmfamily\itshape,
  escapeinside={||},
  frame=tb,
  keepspaces=true,
  keywordstyle=\bfseries,
  language=ceu,
  mathescape=true,
  numbersep=4pt,
  numberstyle=\scriptsize,
  upquote=true,
}

>>>>

\usepackage{listings}
\lstdefinelanguage{ceu}{%
  language=C,
  morekeywords={%
    and, uint32_t, code, async, isr,
    await, bool, call, class, data, define, deterministic, do, each, else,
    emit, end, escape, event, every, finalize, hor, implementation, in,
    input, interface, loop, min, native, new, nohold, not, or, output, par,
    pool, pure, return, signal, spawn, tag, then, this, traverse, until,
    var, watching, when, with},
}
\lstset{
  basicstyle=\ttfamily,
  captionpos=b,
  columns=flexible,
  commentstyle=\rmfamily\itshape,
  escapeinside={||},
  escapeinside={|},
  frame=tb,
  keepspaces=true,
  keywordstyle=\bfseries,
  language=ceu,
  mathescape=true,
  numbersep=4pt,
  numberstyle=\scriptsize,
  upquote=true,
}
